%-------------------------------------------------------------------------------
% SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Education}

\vspace{-2mm}

%-------------------------------------------------------------------------------
% CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  
\cventry
  {M.S. in Computer Science and Engineering} % Degree
  {National Yang Ming Chiao Tung University (NYCU)} % Institution
  {Hsinchu, Taiwan} % Location
  {Sep. 2019 - May. 2022} % Date(s)
  {
    \begin{cvitems} % Description(s) bullet points
      \item {GPA: 4.11/4.3. Previous school name is \textbf{National Chiao Tung University (NCTU)}}
      \item {Thesis: "Offworker: An Offloading Framework for Parallel Web Applications".
      The first study for offloading parallel web applications to cloud via web workers,
      which can improve web apps performance up to 5x on a mobile device.
      The research has been published at the WISE'22 conference.
      }
    \end{cvitems}
  }

  \vspace{-3mm}

\cventry
    {M.S. Exchange Program in Computer Science and Engineering} % Degree
    {Polytechnic University of Milan} % Institution
    {Milan, Italy} % Location
    {Sep. 2021 - Feb. 2022} % Date(s)
    {}

  \vspace{-6mm}

  \cventry
    {B.S. in Bio-Industrial Mechatronics Engineering} % Degree
    {National Taiwan University (NTU)} % Institution
    {Taipei, Taiwan} % Location
    {Sep. 2014 - Jun. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Thesis: A machine learning model of efficient website rendering for server rendering browser.
          Proposed a model to guess which parts of the website need to be re-rendered so that reduces rendering time
          and optimize web performance. GPA: 3.10/4.3. 
        }
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
