%-------------------------------------------------------------------------------
% SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}

%-------------------------------------------------------------------------------
% CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
    \cventry
    {Senior Software Engineer} % Job title
    {T2, Inc.} % Organization
    {Hybrid} % Location
  {Nov. 2025 -- Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led a \textbf{two-person project} to develop a \textbf{QA cluster platform} from scratch for running T2's simulation tools. Designed the system architecture and implemented the software stack with \textbf{Kubernetes} and \textbf{Docker}, the backend in \textbf{Golang}, and the frontend in \textbf{React}. Also designed and built the underlying cluster hardware.}
        \item {Designed and implemented an \textbf{OpenDrive-like} mapping system and an \textbf{OpenScenario-like} scenario definition system, supporting various types of maps and scenarios to perform closed-loop simulation with the autonomous driving planning system.}
      \end{cvitems}
    }

    \vspace{2mm}
  %---------------------------------------------------------


    \cventry
    {Technical Co-founder} % Job title
    {Datra AI} % Organization
    {Remote} % Location
  {Feb. 2025 -- Sep. 2025} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Co-founded an AI startup building an \textbf{AI chatbot} with an inbox system for \textbf{Shopify} merchants in the skincare industry.}
    \item {Led end-to-end product development, including infrastructure, system architecture, backend (\textbf{Golang}), frontend (\textbf{React}), \textbf{AI engineering}, and deployment on \textbf{AWS} with \textbf{Docker}.}
    \item {Built an \textbf{AI system} integrating various \textbf{LLMs} (e.g., OpenAI, Claude), with optimized \textbf{prompt engineering} and retrieval-augmented generation (\textbf{RAG}) techniques.}
    \item {Collaborated with the business co-founder and managed up to \textbf{2 part-time developers} who assisted with product development and maintenance.}
      \end{cvitems}
    }

    \vspace{2mm}

  %---------------------------------------------------------
  \cventry
      {Backend Software Engineer} % Job title
    {Mujin, Inc.} % Organization
      {Tokyo, Japan} % Location
    {Sep. 2022 -- May 2025} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a universal \textbf{network device discovery service} in \textbf{C++} using \textbf{PcapPlusPlus} that detects IP devices (robots, \textbf{industrial cameras}, etc.) on the network within seconds.}
        \item {Developed a \textbf{real-time live streaming and playback system} supporting over \textbf{100} surveillance cameras with latency under \textbf{50 ms}, based on \textbf{FFmpeg}, \textbf{WebRTC}, and \textbf{Golang}.}
        \item {Maintained the robot and warehouse systems written in \textbf{C++} and \textbf{Python}, using \textbf{ZMQ} and \textbf{Qt/QML}.}
        \item {Implemented new \textbf{web APIs} (\textbf{Golang}) and \textbf{ZMQ} APIs (\textbf{C++}) to support frontend projects and internal system services.}
        \item {Designed internal web-based UI tools using \textbf{Figma} and \textbf{React}.}
      \end{cvitems}
    }

    \vspace{2mm}

%---------------------------------------------------------
  % \cventry
  %   {Teaching Assistant} % Job title
  %   {National Yang Ming Chiao Tung University} % Organization
  %   {Hsinchu, Taiwan} % Location
  %   {2019 - 2021} % Date(s)
  %   {
  %     \begin{cvitems} % Description(s) of tasks/responsibilities
  %       \item {Parallel Programming (Spring 2021, Fall 2020). Won the \textbf{NYCU outstanding teaching assistant award} in 2021.
  %       Led a four-TA team to serve a 120-student course, including designing programming assignments,
  %       providing workplace environments, and interacting with students.
  %       }
  %       \item {Numerical Software Development (Spring 2021, Fall 2020, Spring 2020, Fall 2019).
  %       Reviewed and scored students' programming assignments on Github.
  %       }
  %     \end{cvitems}
  %   }

  %   % \vspace{-2mm}
\end{cventries}
