%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Open-Source Projects}

\vspace{-2mm}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {} % Affiliation/role
    {PcapPlusPlus} % Organization/group
    {} % Location
    {} % Date(s)
    {
      \vspace{-2mm}
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {PcapPlusPlus is a multiplatform \textbf{C++} library for capturing, parsing and crafting of network packets.}
        \item {While developing Mujin network service using PcapPlusPlus, I found many places in PcapPlusPlus can be improved,
        so I keep contributing to this project, providing new features and bug fixes.}
        \item {I was granted as a \textbf{maintainer} of the project from Feb, 2024.}
        \item {I have been actively maintaining the project, reviewing pull requests, and providing technical support to users, including reviewing about 100 PRs, 23 PR merged.}
        \item {Project link: \url{https://github.com/seladb/PcapPlusPlus/}.}
      \end{cvitems}
    }
  \vspace{-2mm}

  \cventry
    {} % Affiliation/role
    {modmesh} % Organization/group
    {} % Location
    {} % Date(s)
    {
      \vspace{-2mm}
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item { modmesh is a toolkit for solving partial differential equations. It is written in \textbf{C++} and \textbf{Pybind11} for high-Performance
        numerical computing.}
        \item { This project is contributed by many Taiwanese software engineers in semiconductor industry for fun. We aim to develop the fastest and the most efficient numerical toolkit and we like to test new ideas on it.}
        \item {I am an active contributor with about 45 PRs merged.}
        \item {Project link: \url{https://github.com/solvcon/modmesh}.}
      \end{cvitems}
    }
    \vspace{-2mm}

  \cventry
    {} % Affiliation/role
    {node-color-log} % Organization/group
    {} % Location
    {} % Date(s)
    {
      \vspace{-2mm}
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {
          I developed and maintained a lightweight \textbf{JavaScript} logger with \textbf{220k/month} downloads,
          which provides an alternative solution to existing mature counterparts which usually have a huge codebase.
        }
        \item {Project link: \url{https://github.com/tigercosmos/node-color-log}.}
      \end{cvitems}
    }
    \vspace{-2mm}

\end{cventries}
